---
title: "Exploring SES and Childcare attendance effect on learning outcomes"
author: "Maria Prokofieva"
title-block-banner: "images/hero.jpeg"
format: 
  html:
    theme: cosmo
    social: ["twitter", "facebook", "linkedin"]
    code-fold: true
    page-layout: full
    fig_caption: yes
---

<style>

.quarto-title-banner{
  margin-block-end: 1rem;
  position: relative;
  margin-top: -30px;
  height: 100%
}
</style>

```{r}
library(tidyverse)
library(gt)
library(reactable)
library(afex)

#Call emmeans
library(emmeans)
library(viridis)


theme_set(theme_minimal())



data<-read_csv("/Volumes/TOSHIBA EXT/LSAC/Project_data/waves4_9_childcare2.csv")

#data$literacy_index2<-data$literacy_index[,1]

#data$numeracy_index2<-data$numeracy_index[,1]
#data$academic_index2<-data$academic_index[,1]

#data2<-data|>select(
#  -c(literacy_index, numeracy_index, academic_index)
#)
#data2|>write_csv("/Volumes/TOSHIBA EXT/LSAC/Project_data/waves4_9_childcare2.csv")

```

## Childcare attendace in wave 1 (age = 3-19months) 

### Looked by others in wave 1

```{r}

data|>filter(wave==4)|>count(childcare_w1, ses_w1)|>
  mutate(
    childcare=case_when(
      childcare_w1==1~"Yes",
      TRUE~"No"
    ))|>
  reactable()

data|>filter(wave==4)|>count(childcare_w1, ses_w1)|>
  mutate(
    childcare=case_when(
      childcare_w1==1~"Yes",
      TRUE~"No"
    ))|>
  ggplot(
    aes(childcare, n, fill=ses_w1)
  )+
  geom_col()+
  labs(
    title="Looked by others in wave 1 (age = 3-19months)",
    x="Non-parental care",
    y="Number of children",
    fill="SES"
  )
```


### Daycare center attendace


```{r}

data|>filter(wave==4)|>count(childcare_daycare_w1, ses_w1)|>
  mutate(
    childcare=case_when(
      childcare_daycare_w1==1~"Yes",
      TRUE~"No"
    ))|>
  reactable()

data|>filter(wave==4)|>count(childcare_daycare_w1, ses_w1)|>
  mutate(
    childcare=case_when(
      childcare_daycare_w1==1~"Yes",
      TRUE~"No"
    ))|>
  ggplot(
    aes(childcare, n, fill=ses_w1)
  )+
  geom_col()+
  labs(
    title="Daycare attendance in wave 1 (age = 3-19months)",
    x="Daycare attendance",
    y="Number of children",
    fill="SES"
  )

```

## Childcare attendace in wave 2 (age = 2-3 years) - Looked by others in wave 2

```{r}

data|>filter(wave==4)|>count(childcare_w2, ses_w2)|>
  mutate(
    childcare=case_when(
      childcare_w2==1~"Yes",
      TRUE~"No"
    ))|>
  reactable()

data|>filter(wave==4)|>count(childcare_w2, ses_w2)|>
  mutate(
    childcare=case_when(
      childcare_w2==1~"Yes",
      TRUE~"No"
    ))|>
  ggplot(
    aes(childcare, n, fill=ses_w2)
  )+
  geom_col()+
  labs(
    title="Looked by others in wave 2 (age = 2-3 years)",
    x="Non-parental care",
    y="Number of children",
    fill="SES"
  )

```

### Daycare center attendace


```{r}

data|>filter(wave==4)|>count(childcare_daycare_w2, ses_w2)|>
  mutate(
    childcare=case_when(
      childcare_daycare_w2==1~"Yes",
      TRUE~"No"
    ))|>
  reactable()

data|>filter(wave==4)|>count(childcare_daycare_w2, ses_w2)|>
  mutate(
    childcare=case_when(
      childcare_daycare_w2==1~"Yes",
      TRUE~"No"
    ))|>
  ggplot(
    aes(childcare, n, fill=ses_w2)
  )+
  geom_col()+
  labs(
    title="Daycare attendance in wave 2 (age = 2-3 years)",
    x="Daycare attendance",
    y="Number of children",
    fill="SES"
  )

```

### Preschool/kinder attendace


```{r}

data|>filter(wave==4)|>count(childcare_kinder_w2, ses_w2)|>
  mutate(
    childcare=case_when(
      childcare_kinder_w2==1~"Yes",
      TRUE~"No"
    ))|>
  reactable()

data|>filter(wave==4)|>count(childcare_kinder_w2, ses_w2)|>
  mutate(
    childcare=case_when(
      childcare_kinder_w2==1~"Yes",
      TRUE~"No"
    ))|>
  ggplot(
    aes(childcare, n, fill=ses_w2)
  )+
  geom_col()+
  labs(
    title="Preschool/kinder attendace in wave 2 (age = 2-3 years)",
    x="Preschool/kinder attendace",
    y="Number of children",
    fill="SES"
  )

```

## Non-parental care - wave 3

### Preschool/kinder attendace (age = 4-5 years)

```{r}

data|>filter(wave==4)|>count(childcare_kinder_w3, ses_w3)|>
  mutate(
    preschool=case_when(
      childcare_kinder_w3==1~"Yes",
      TRUE~"No"
    ))|>
  reactable()

data|>filter(wave==4)|>count(childcare_kinder_w3, ses_w3)|>
  mutate(
    preschool=case_when(
      childcare_kinder_w3==1~"Yes",
      TRUE~"No"
    ))|>
  ggplot(
    aes(preschool, n, fill=ses_w3)
  )+
  geom_col()+
  labs(
    title="Preschool/kinder attendace in wave 3 (age = 4-5 years)",
    x="Preschool/kinder attendace",
    y="Number of children",
    fill="SES"
  )

```

### At school (age = 4-5 years)

```{r}

data|>filter(wave==4)|>count(school_w3, ses_w3)|>
  mutate(
    at_school=case_when(
      school_w3==1~"Yes",
      TRUE~"No"
    ))|>
  reactable()

data|>filter(wave==4)|>count(school_w3, ses_w3)|>
  mutate(
    at_school=case_when(
      school_w3==1~"Yes",
      TRUE~"No"
    ))|>
  ggplot(
    aes(at_school, n, fill=ses_w3)
  )+
  geom_col()+
  labs(
    title="At school in wave 3 (age = 4-5 years)",
    x="School attendace",
    y="Number of children",
    fill="SES"
  )

```


## Mean Naplan scores by SES

### Naplan Year 3 (wave 5)

```{r}

data|>filter(wave==5)|>
  group_by(
    ses
  )|>
  summarise(
    mean_reading=round(mean(naplan_reading, na.rm=TRUE),2),
    mean_writing=round( mean(naplan_writing, na.rm=TRUE),2),
    mean_spelling=round(mean(naplan_spelling, na.rm=TRUE),2),
    mean_grammar=round(mean(naplan_grammar, na.rm=TRUE),2),
    mean_numeracy=round(mean(naplan_numeracy, na.rm=TRUE),2)
    )|>
  reactable()
    
```

```{r}
#boxplot

data|>filter(wave==5)|>
  filter(!is.na(ses))|>
  pivot_longer(
    cols=c(naplan_reading, naplan_writing, naplan_spelling, naplan_grammar, naplan_numeracy),
    names_to="domain",
    values_to="score"
  )|>
  ggplot(aes (x=ses, y=score, color=ses))+geom_boxplot()+
  facet_wrap(~domain, scales="free")+
  labs(
    title="Naplan scores by SES - year 3",
    x="SES",
    y="Naplan score"
  )

```


### Naplan Year 5 (wave 6)

```{r}

data|>filter(wave==6)|>
  group_by(
    ses
  )|>
  summarise(
    mean_reading=round(mean(naplan_reading, na.rm=TRUE),2),
    mean_writing=round( mean(naplan_writing, na.rm=TRUE),2),
    mean_spelling=round(mean(naplan_spelling, na.rm=TRUE),2),
    mean_grammar=round(mean(naplan_grammar, na.rm=TRUE),2),
    mean_numeracy=round(mean(naplan_numeracy, na.rm=TRUE),2)
    )|>
  reactable()
    
```

```{r}
#boxplot

data|>filter(wave==6)|>
  filter(!is.na(ses))|>
  pivot_longer(
    cols=c(naplan_reading, naplan_writing, naplan_spelling, naplan_grammar, naplan_numeracy),
    names_to="domain",
    values_to="score"
  )|>
  ggplot(aes (x=ses, y=score, color=ses))+geom_boxplot()+
  facet_wrap(~domain, scales="free")+
  labs(
    title="Naplan scores by SES - year 5",
    x="SES",
    y="Naplan score"
  )

```


### Naplan Year 7 (wave 7)

```{r}

data|>filter(wave==7)|>
  group_by(
    ses
  )|>
  summarise(
    mean_reading=round(mean(naplan_reading, na.rm=TRUE),2),
    mean_writing=round( mean(naplan_writing, na.rm=TRUE),2),
    mean_spelling=round(mean(naplan_spelling, na.rm=TRUE),2),
    mean_grammar=round(mean(naplan_grammar, na.rm=TRUE),2),
    mean_numeracy=round(mean(naplan_numeracy, na.rm=TRUE),2)
    )|>
  reactable()
    
```

```{r}
#boxplot

data|>filter(wave==7)|>
  filter(!is.na(ses))|>
  pivot_longer(
    cols=c(naplan_reading, naplan_writing, naplan_spelling, naplan_grammar, naplan_numeracy),
    names_to="domain",
    values_to="score"
  )|>
  ggplot(aes (x=ses, y=score, color=ses))+geom_boxplot()+
  facet_wrap(~domain, scales="free")+
  labs(
    title="Naplan scores by SES - year 7",
    x="SES",
    y="Naplan score"
  )

```

### Naplan Year 9 (wave 8)

```{r}

data|>filter(wave==8)|>
  group_by(
    ses
  )|>
  summarise(
    mean_reading=round(mean(naplan_reading, na.rm=TRUE),2),
    mean_writing=round( mean(naplan_writing, na.rm=TRUE),2),
    mean_spelling=round(mean(naplan_spelling, na.rm=TRUE),2),
    mean_grammar=round(mean(naplan_grammar, na.rm=TRUE),2),
    mean_numeracy=round(mean(naplan_numeracy, na.rm=TRUE),2)
    )|>
  reactable()
    
```

```{r}
#boxplot

data|>filter(wave==8)|>
  filter(!is.na(ses))|>
  pivot_longer(
    cols=c(naplan_reading, naplan_writing, naplan_spelling, naplan_grammar, naplan_numeracy),
    names_to="domain",
    values_to="score"
  )|>
  ggplot(aes (x=ses, y=score, color=ses))+geom_boxplot()+
  facet_wrap(~domain, scales="free")+
  labs(
    title="Naplan scores by SES - year 9",
    x="SES",
    y="Naplan score"
  )

```


## Post School  (wave 9)

### Enrolled in institution/ attend secondary school

```{r}

res<-data|>filter(wave==9)|>
  count(
    ses, enrolled_institution
  )|>
  mutate(
    enrolled_institution=case_when(
      enrolled_institution==1~"Secondary school",
      enrolled_institution==2~"TAFE",
      enrolled_institution==3~"University",
      enrolled_institution==4~"Other",
      TRUE~"NA"
    )
  )

res|>reactable()
```

```{r}

res|>filter(!is.na(ses))|>
  
  ggplot(aes(x=ses, y=n, fill=enrolled_institution))+
  geom_bar(stat="identity", position="dodge")+
  labs(
    title="Post school enrolment by SES",
    x="SES",
    y="Number of students"
  )

```

### Intended qualification

```{r}

res<-data|>filter(wave==9)|>
  count(
    ses, enrolled_degree
  )|>
  mutate(
    enrolled_degree=case_when(
      enrolled_degree==1~"Bachelor degree",
      enrolled_degree==2~"Advanced diploma or diploma",
      enrolled_degree==3~"Certificate",
      enrolled_degree==4~"Other",
      TRUE~"NA"
    )
  )

```


#-----------------------------

## Interaction effect - Two-way Anova - Ability X SES

### Academic scores (academic_index) X SES per wave

```{r}
#Perform the ANOVA
data_res<-data|>filter(!is.na(ses_w1) & !is.na(academic_index2) & !is.na(wave))

model_1 <- aov_car(academic_index2 ~ (wave*ses_w1) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~ses_w1)
res_wave_group <- emmeans(model_1, specs = ~wave*ses_w1)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = ses_w1, group = ses_w1)) +
  geom_point(aes(color = ses_w1)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+
  labs(
    title="Academic scores by SES and wave",
    x="Wave",
    y="Academic score"
  )

```

### Literacy scores (literacy_index) X SES per wave

```{r}

#Perform the ANOVA
data_res<-data|>filter(!is.na(ses_w1) & !is.na(literacy_index2) & !is.na(wave))

model_1 <- aov_car(literacy_index2 ~ (wave*ses_w1) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~ses_w1)
res_wave_group <- emmeans(model_1, specs = ~wave*ses_w1)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = ses_w1, group = ses_w1)) +
  geom_point(aes(color = ses_w1)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+labs(
    title="Literacy scores by SES",
    x="Wave",
    y="Literacy score"
  )

```

### Numeracy scores (numeracy_index) X SES per wave

```{r}

#Perform the ANOVA
data_res<-data|>filter(!is.na(ses_w1) & !is.na(numeracy_index2) & !is.na(wave))

model_1 <- aov_car(numeracy_index2 ~ (wave*ses_w1) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~ses_w1)
res_wave_group <- emmeans(model_1, specs = ~wave*ses_w1)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = ses_w1, group = ses_w1)) +
  geom_point(aes(color = ses_w1)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+labs(
    title="Numeracy scores by SES",
    x="Wave",
    y="Numeracy score"
  )

```

----------

----------

## Interaction effect - Two-way Anova - Ability X Daycare attendance (w1)

### Academic scores (academic_index) X S Daycare attendance (w1) 

```{r}
#Perform the ANOVA
data_res<-data|>filter(!is.na(childcare_daycare_w1) & !is.na(academic_index2) & !is.na(wave))

model_1 <- aov_car(academic_index2 ~ (wave*childcare_daycare_w1) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~childcare_daycare_w1)
res_wave_group <- emmeans(model_1, specs = ~wave*childcare_daycare_w1)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = childcare_daycare_w1, group = childcare_daycare_w1)) +
  geom_point(aes(color = childcare_daycare_w1)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+
  labs(
    title="Academic scores by Daycare in w1 and wave",
    x="Wave",
    y="Academic score  
    "
  )

```

### Literacy scores (literacy_index) X Daycare in w1 per wave

```{r}

#Perform the ANOVA
data_res<-data|>filter(!is.na(childcare_daycare_w1) & !is.na(literacy_index2) & !is.na(wave))

model_1 <- aov_car(literacy_index2 ~ (wave*childcare_daycare_w1) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~childcare_daycare_w1)
res_wave_group <- emmeans(model_1, specs = ~wave*childcare_daycare_w1)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = childcare_daycare_w1, group = childcare_daycare_w1)) +
  geom_point(aes(color = childcare_daycare_w1)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+labs(
    title="Literacy scores by Daycare attendance in w1 and wave",
    x="Wave",
    y="Literacy score"
  )

```

### Numeracy scores (numeracy_index) X Daycare w1 per wave

```{r}

#Perform the ANOVA
data_res<-data|>filter(!is.na(childcare_daycare_w1) & !is.na(numeracy_index2) & !is.na(wave))

model_1 <- aov_car(numeracy_index2 ~ (wave*childcare_daycare_w1) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~childcare_daycare_w1)
res_wave_group <- emmeans(model_1, specs = ~wave*childcare_daycare_w1)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = childcare_daycare_w1, group = childcare_daycare_w1)) +
  geom_point(aes(color = childcare_daycare_w1)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+labs(
    title="Numeracy scores by Childare attendance in w1 and wave",
    x="Wave",
    y="Numeracy score"
  )

```


----------

## Interaction effect - Two-way Anova - Ability X Daycare attendance (w2)

### Academic scores (academic_index) X  Daycare attendance (w2) 

```{r}
#Perform the ANOVA
data_res<-data|>filter(!is.na(childcare_daycare_w2) & !is.na(academic_index2) & !is.na(wave))

model_1 <- aov_car(academic_index2 ~ (wave*childcare_daycare_w2) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~childcare_daycare_w2)
res_wave_group <- emmeans(model_1, specs = ~wave*childcare_daycare_w2)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = childcare_daycare_w2, group = childcare_daycare_w2)) +
  geom_point(aes(color = childcare_daycare_w2)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+
  labs(
    title="Academic scores by Daycare in w2 and wave",
    x="Wave",
    y="Daycare attendance  
    "
  )

```

### Literacy scores (literacy_index) X Daycare in w2 per wave

```{r}

#Perform the ANOVA
data_res<-data|>filter(!is.na(childcare_daycare_w2) & !is.na(literacy_index2) & !is.na(wave))

model_1 <- aov_car(literacy_index2 ~ (wave*childcare_daycare_w2) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~childcare_daycare_w2)
res_wave_group <- emmeans(model_1, specs = ~wave*childcare_daycare_w2)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = childcare_daycare_w2, group = childcare_daycare_w2)) +
  geom_point(aes(color = childcare_daycare_w2)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+labs(
    title="Literacy scores by Daycare attendance in w2 and wave",
    x="Wave",
    y="Literacy score"
  )

```

### Numeracy scores (numeracy_index) X Daycare in w2 per wave

```{r}

#Perform the ANOVA
data_res<-data|>filter(!is.na(childcare_daycare_w2) & !is.na(numeracy_index2) & !is.na(wave))

model_1 <- aov_car(numeracy_index2 ~ (wave*childcare_daycare_w2) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~childcare_daycare_w2)
res_wave_group <- emmeans(model_1, specs = ~wave*childcare_daycare_w2)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = childcare_daycare_w2, group = childcare_daycare_w2)) +
  geom_point(aes(color = childcare_daycare_w2)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+labs(
    title="Numeracy scores by Childare attendance in w2 and wave",
    x="Wave",
    y="Numeracy score"
  )

```

-----------------


## Interaction effect - Two-way Anova - Naplan X SES

### Naplan reading X SES per wave

```{r}
#Perform the ANOVA
data_res<-data|>filter(!is.na(ses_w1) & !is.na(naplan_reading) & !is.na(wave))

model_1 <- aov_car(naplan_reading ~ (wave*ses_w1) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~ses_w1)
res_wave_group <- emmeans(model_1, specs = ~wave*ses_w1)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = ses_w1, group = ses_w1)) +
  geom_point(aes(color = ses_w1)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+
  labs(
    title="Naplan reading by SES and wave",
    x="Wave",
    y="Naplan score"
  )

```

### Naplan numeracy X SES per wave

```{r}
#Perform the ANOVA
data_res<-data|>filter(!is.na(ses_w1) & !is.na(naplan_numeracy) & !is.na(wave))

model_1 <- aov_car(naplan_numeracy ~ (wave*ses_w1) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~ses_w1)
res_wave_group <- emmeans(model_1, specs = ~wave*ses_w1)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = ses_w1, group = ses_w1)) +
  geom_point(aes(color = ses_w1)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+
  labs(
    title="Naplan numeracy by SES and wave",
    x="Wave",
    y="Naplan score"
  )

```
-----------------

## Interaction effect - Two-way Anova - Naplan X Daycare w1

### Naplan reading X SES per wave

```{r}
#Perform the ANOVA
data_res<-data|>filter(!is.na(childcare_daycare_w1) & !is.na(naplan_reading) & !is.na(wave))

model_1 <- aov_car(naplan_reading ~ (wave*childcare_daycare_w1) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~childcare_daycare_w1)
res_wave_group <- emmeans(model_1, specs = ~wave*childcare_daycare_w1)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = childcare_daycare_w1, group = childcare_daycare_w1)) +
  geom_point(aes(color = childcare_daycare_w1)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+
  labs(
    title="Naplan reading by Daycare w1 and wave",
    x="Wave",
    y="Naplan score"
  )

```

### Naplan numeracy X SES per wave

```{r}
#Perform the ANOVA
data_res<-data|>filter(!is.na(childcare_daycare_w1) & !is.na(naplan_numeracy) & !is.na(wave))

model_1 <- aov_car(naplan_numeracy ~ (wave*childcare_daycare_w1) + Error(hicid/wave), 
                    data = data_res)


#Get the output
summary(model_1)


#Calculate estimated marginal means
res_wave <- emmeans(model_1, specs = ~wave)
res_group <- emmeans(model_1, specs = ~childcare_daycare_w1)
res_wave_group <- emmeans(model_1, specs = ~wave*childcare_daycare_w1)

#Look at the estimated means
res_wave_group

ggplot(data = as.data.frame(res_wave_group), aes(x = wave, y = emmean)) +
  geom_line(aes(color = childcare_daycare_w1, group = childcare_daycare_w1)) +
  geom_point(aes(color = childcare_daycare_w1)) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+
  labs(
    title="Naplan numeracy by Daycare w1 and wave",
    x="Wave",
    y="Naplan score"
  )

```
-----------------


